Macroscopic Salt Rejection through Electrostatically Gated Nanoporous Graphene

### 2019-03-06 paper/SI.tex
Correct psiG to VG

Applying a positive $V_{\mathrm{G}}$ changes the surface distribution
of the cations / anions. To see this, we plot the concentrations of
cation ($c_{+}$) and anion ($c_{-}$) near a graphene nanopore with
$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $\psi_{\mathrm{G}}$ =
0.15 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
respectively. The cations are depleted from the graphene surface,
while the anions are accumulated due to positive
$\psi_{\mathrm{G}}$. The anion concentration at the graphene surface
is enhanced $\sim{}$35 times compared with the bulk concentration in
HCR. The thickness of the depletion / accumulation layer is affected
by the bulk concentration. Here we show this by comparing the radial
distribution of $c_{+}$ and $c_{-}$ along the $z = 0$ line within the
graphene pore. \Fig{} \ref{fig:conc-r} shows such radial ionic
concentration distribution at different $c_{0}$ and $V_{\mathrm{G}}$
levels. When $c_{0}$ = 0.1 mM, $\lambda_{\mathrm{D}}$ is larger than
$r_{\mathrm{G}}$, and the external gate voltage $V_{\mathrm{G}}$ has
control over both $c_{-}$ and $c_{+}$ within the graphene nanopore
(\Fig{} \ref{fig:conc-r}a and \ref{fig:conc-r}c). On the other
hand, when $c_{0}$ = 100 mM, $\lambda_{\mathrm{D}}$ is much smaller
than $r_{\mathrm{G}}$, and the concentration is only affected by
$V_{\mathrm{G}}$ close to the pore edge (\Fig{} \ref{fig:conc-r}b
and \ref{fig:conc-r}d). Therefore by increasing $c_{0}$ (and
equivalently reducing $\lambda_{\mathrm{D}}$), $V_{\mathrm{G}}$ loses
control over the transport in the center of the pore and leads to a
lower $\xi$ value. Due to the existence of graphene quantum
capacitance, the surface potential $\psi_{\mathrm{G}}$ is essentially
smaller than $V_{\mathrm{G}}$, and the maximum surface anion
concentration ($c_{0}$ = 100 mM, $V_{\mathrm{G}}$ = 1.25 V) is
$\sim{}$3 M, much smaller than the saturated surface adsorption
density (at the order of 10$^{2}$ M
\cite{bard_electrochemical_1980}). Therefore we expect the surface
enhancement of the anions under the FEM conditions to be realistic and
the influence of the anion concentration on the diffusivity is minimal
\cite{Tang_1999_I}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-concentration.pdf}
  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore
    with $r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM, and
    $\psi_{\mathrm{G}}$ = 0.15 V, for a KCl solution at 0.1
    mM. Depletion of cation and accumulation of anion can be observed
    near the graphene surface.}
  \label{fig:conc}
\end{figure}

@@

Next we analyze the diffusion and drift contributions to the ionic
transport. As shown in \Fig{} \ref{fig:potential}, the
electrochemical potential energy $\mu_{i}$ is decomposed into the
electric potential energy $z_{i} c_{i} \psi_{i}$ (\Fig{}
\ref{fig:potential}a and \ref{fig:potential}b) and the chemical
potential energy $k_{\mathrm{B}}T \ln x_{i}$ (\Fig{}
\ref{fig:potential}c and \ref{fig:potential}d) near a graphene
nanopore with $r_{\mathrm{G}}$ = 10 nm and $\psi_{\mathrm{G}}$ = 0.15
V. The transport of cations is dominated by its chemical potential and
the diffusion is prominent in the center of the pore. On the other
hand, the electric and diffusive potential energies are similar with
opposite signs and counterbalance each other. This explains the
relatively smaller electrochemical potential of anions in main text
\Fig{} \ref{main-fig:4}b. As a result, different pathways for cations
and anions emerge that cations preferably pass through the pore
center, while anions mainly pass near the pore edge, as shown in
\Fig{} \ref{fig:flux}.

>>>>

Applying a positive $V_{\mathrm{G}}$ changes the surface distribution
of the cations / anions. To see this, we plot the concentrations of
cation ($c_{+}$) and anion ($c_{-}$) near a graphene nanopore with
$r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM and $V_{\mathrm{G}}$ =
0.75 V, as shown in \Fig{} \ref{fig:conc}a and \ref{fig:conc}b,
respectively. The cations are depleted from the graphene surface,
while the anions are accumulated due to positive
$\psi_{\mathrm{G}}$. The anion concentration at the graphene surface
is enhanced $\sim{}$35 times compared with the bulk concentration in
HCR. The thickness of the depletion / accumulation layer is affected
by the bulk concentration. Here we show this by comparing the radial
distribution of $c_{+}$ and $c_{-}$ along the $z = 0$ line within the
graphene pore. \Fig{} \ref{fig:conc-r} shows such radial ionic
concentration distribution at different $c_{0}$ and $V_{\mathrm{G}}$
levels. When $c_{0}$ = 0.1 mM, $\lambda_{\mathrm{D}}$ is larger than
$r_{\mathrm{G}}$, and the external gate voltage $V_{\mathrm{G}}$ has
control over both $c_{-}$ and $c_{+}$ within the graphene nanopore
(\Fig{} \ref{fig:conc-r}a and \ref{fig:conc-r}c). On the other
hand, when $c_{0}$ = 100 mM, $\lambda_{\mathrm{D}}$ is much smaller
than $r_{\mathrm{G}}$, and the concentration is only affected by
$V_{\mathrm{G}}$ close to the pore edge (\Fig{} \ref{fig:conc-r}b
and \ref{fig:conc-r}d). Therefore by increasing $c_{0}$ (and
equivalently reducing $\lambda_{\mathrm{D}}$), $V_{\mathrm{G}}$ loses
control over the transport in the center of the pore and leads to a
lower $\xi$ value. Due to the existence of graphene quantum
capacitance, the surface potential $\psi_{\mathrm{G}}$ is essentially
smaller than $V_{\mathrm{G}}$, and the maximum surface anion
concentration ($c_{0}$ = 100 mM, $V_{\mathrm{G}}$ = 1.25 V) is
$\sim{}$3 M, much smaller than the saturated surface adsorption
density (at the order of 10$^{2}$ M
\cite{bard_electrochemical_1980}). Therefore we expect the surface
enhancement of the anions under the FEM conditions to be realistic and
the influence of the anion concentration on the diffusivity is minimal
\cite{Tang_1999_I}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-concentration.pdf}
  \caption{Cation concentration $c_{+}$ (\textbf{a}.) and anion
    concentration $c_{-}$ (\textbf{b}.) near the graphene nanopore
    with $r_{\mathrm{G}}$ = 10 nm, $c_{0}$ = 0.1 mM, and
    $V_{\mathrm{G}}$ = 0.75 V, for a KCl solution at 0.1
    mM. Depletion of cation and accumulation of anion can be observed
    near the graphene surface.}
  \label{fig:conc}
\end{figure}

@@

Next we analyze the diffusion and drift contributions to the ionic
transport. As shown in \Fig{} \ref{fig:potential}, the
electrochemical potential energy $\mu_{i}$ is decomposed into the
electric potential energy $z_{i} c_{i} \psi_{i}$ (\Fig{}
\ref{fig:potential}a and \ref{fig:potential}b) and the chemical
potential energy $k_{\mathrm{B}}T \ln x_{i}$ (\Fig{}
\ref{fig:potential}c and \ref{fig:potential}d) near a graphene
nanopore with $r_{\mathrm{G}}$ = 10 nm and $V_{\mathrm{G}}$ = 0.75
V. The transport of cations is dominated by its chemical potential and
the diffusion is prominent in the center of the pore. On the other
hand, the electric and diffusive potential energies are similar with
opposite signs and counterbalance each other. This explains the
relatively smaller electrochemical potential of anions in main text
\Fig{} \ref{main-fig:4}b. As a result, different pathways for cations
and anions emerge that cations preferably pass through the pore
center, while anions mainly pass near the pore edge, as shown in
\Fig{} \ref{fig:flux}.
